The responses of \textit{\textit{Spinifex littoreus}} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China

### 2021-01-03 tex/interactcsesample.tex
slightly rectified by Du's comments

\label{Introduction-4}
% 这一段主要介绍老鼠乐与研究去意义
\textit{Spinifex littoreus}, a herbaceous plant, is the dominant species in coastal foredunes in South China. It often grows vigorously in the more dynamic foredune, while it declines in the more stabilized backdunes in similarity to its Australian and NZ cousins \textit{S. hirsutus} and \textit{S. sericeus} \citep{hespReviewBiologicalGeomorphological1989}. Its peak growth occurs in summer, with two growth forms, including elongation of horizontal stolons and upward growth of vertical ramets, which sprout out from the same vegetative reproduction, and usually can be recognized as the same ramets \citep{jacksonPopulationBiologyEvolution1985}. The leaf apex of \textit{S. littoreus} is very sharp and hard, which makes it difficult to be intruded, and is usually recognized as one of the excellent species for sand dune fixation in this region \citep{yangDiurnalvariationcharacteristics2017}. Frequent typhoons often occur in the growing season of this species in South China, which causes severe sand burial on \textit{S. littoreus}, particularly its stolons on nebkhas (a sand dune that forms around vegetation) forming the foredune zone \citep{yangDiurnalvariationcharacteristics2017}(Figure~\ref{fig:sample-pic}a). However, the tolerance capacity of this species to sand burial is still unclear at present, and how this species revitalized in the sand burial caused by frequent typhoon events in growing season. Furthermore, local government has planted an invasive species \textit{Casuarinas equisetifolia} for the stabilization of nebkhas originally formed by \textit{S. littoreus}, which causes severe damage to this native species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure~\ref{fig:sample-pic}b). Therefore, understanding the adaptive strategies of \textit{S. littoreus} to sand burial levels, and its role in the stabilization of coastal sand dunes are very crucial for the effective coastal management and conservation in South China.

\begin{figure}
  \centering
  \subfloat[\textit{S. littoreus} was burial after a typhoon.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/sand_buried_plants.png}}}\hspace{5pt}
  \subfloat[\textit{S. littoreus} nebkhas was eradicated and planted with \textit{C. equisetifolia}.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/damaged_trees.jpg}}}
  \caption{(a) Intensive sand burial on the \textit{Spinifex littoreus} nebkhas on Pingtan Island after typhoon Soudelor (1513) landed in Putian City, Fujian Province, China in August, 2015. (b) The nebkhas formed by \textit{Spinifex littoreus} was stabilized by the planting of an invasive species Casuarinas equisetifolia seedlings on Pingtan Island, Fujian Province, China.} 
  \label{fig:sample-pic}
\end{figure}

\label{Introduction-5}
% 我们的研究假设和研究思路
% 我们认为不同的沙埋情形将改变植株的生长方式，是该植物能够适应台风带来的强烈沙埋的关键性因素。
In this study, we assume that the growths of \textit{S. littoreus} can be facilitated with the increase of sand burial, which is probably the key factor for this native plant to adapt to the intense sand burial caused by frequent typhoon events in growing season. Then, the vertical height of ramets, horizontal length of stolons, and biomass allocation of adventitious roots, stems and leaves on stolons of \textit{S. littoreus} under different sand burial levels were simulated and measured in a field experiment, in a growing season on Pingtan Island, Fujian Province, South China.

@@

\subsection{Methods}
Field experiments were carried out in July, 2016, in Tannan bay, Pingtan Island (Figure~\ref{fig:map}). One study belt without the interruption of animals, pollutants, and apparent human activities was selected in the center of the coastal sand dunes. 
Considering most of the \textit{S. littoreus} were distributed on the windward slope of nebkhas in mobile dunes belt, 35 healthy plants with uniform size were selected for study on this slope (Figure\ref{fig:leeward_swale}). All the observed plants can be well distinguished from surrounding plants, the height of vertical ramets and the length of stolons were all similar with each other before the burial treatments. Stolons of \textit{S. littoreus} on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stem base to the top of the stolons. All plant species around the selected plants were manually cleared, and wooden frames $20 cm$ in height (similar to the height of stolons) were set around the selected plants. Later, all the observed plants were fixed with a label, and its serial number was recorded on the label and wooden baffles respectively in order to facilitate the periodic measurements later. The few adventitious roots present on the stolons of the observed plants were completely eliminated, the height of vertical ramets and length of stolons were measured separately before the experiments began. Later, all the plants were buried with sand nearby artificially (Figure~\ref{fig:diagram}, Table~\ref{tab:treatment}), While control groups (CG) were unburied throughout the experiments.

@@

\begin{figure}[!h]
  \centering
  \subfloat[Developmental period.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9a.jpg}}}\hspace{5pt}
  \subfloat[Stabilized period.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9b.jpg}}}
  \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b). (Photo was taken in Pingtan Island)} 
  \label{fig:added}
\end{figure}

Extensive colonization of horizontal stolons after sand burial will facilitate the plants to increase its capacity for utilization of water and nutrition, which is especially critical for the establishment of plants in a resource-poor environment, such as coastal sand dunes, and further enhance their growth as the dominant species in coastal sand dunes \citep{divyasreeEcologicalStudyReproduction2019,mendoza-gonzalezBiologicalFloraCoastal2014}. Our results indicated that all sand burial treatments had a significant promotion on the  stolon growth, and complete sand burial had more obvious influence than half sand burial. Species usually stimulate their growing point according to the signal of the gravity signal stresses \citep{zhouAnalysisgrowthstrategy2015}, and increase their node number and internode length to escape this physical barrier \citep{maunEffectsBurialSand1996}. The stresses signal of gravity signal in complete sand burial was usually stronger than it in half sand burial \citep{wangAdvancesStudiesMorphological2005}. This was consistent with our field investigation, we found that the tall remets of \textit{S. littoreus} could intercept sand sediments, and its conjoint stolons were buried at different levels on nebkhas. The stolon length of \textit{S. littoreus} on nebkhas in developmental period was much longer than it in stabilized period, which can be attributed to the more dynamic sand movement on the fomer (Figure~\ref{fig:added}).

Production of adventitious roots on the stolons will enhance the capacity of plants to use limited soil water and nutrition, and change the biomass and growth rhythms of plants \citep{martinezResponsesDuneMosses1999,dechAdventitiousRootProduction2006}. Our results indicated that the adventitious roots were produced on the \textit{S. littoreus} stolons in most of the sand burial treatments, both total length and number of roots were increased compared with the CG treatments, which will facilitate their revitalization from sand burial cause by typhoon events. More adventitious roots were allocated to the stolon base after sand burial. Generally, sand burial depth is deeper on the stolon base than other stolon sections due to more sand sediments accumulated around the conjoint ramets, which will increase the capacity for root growth and can improve their access to soil water \citep{yuanEffectsSandAccretion1993}. Moreover, \textit{S.littoreus} has a fibrous root system, and adventitious roots are initially produced from the primordium in the stolon node. However, only the primordium in the stolon base can develop well and finally break through the cuticular layer to produce the adventitious roots \citep{hochholdingerWeedsCropsGenetic2004}.

@@

% 凭借上述机制，我们的结果表明老鼠楽能够有效在近地表被严重的沙埋情况下加速生长并存活下来。在热带和亚热带地区的海岸，频繁的台风常常为迎风坡带来数十厘米厚的沙埋，尽管这样的沙埋足以阻止大多数植物在此生长，但老鼠楽凭借其独特的适应能力在此占据来绝对优势。
Response of plants to sand burial is usually species specific, and the growth of plants will be enhanced under optimal sand burial rate \citep{noletUAVimagingModelGrowth2018}. We found that \textit{S.littoreus} can adapt to the severe sand burial caused by frequent typhoons in our study area, and will revitalize later by increasing the horizontal stolon length, producing abundant adventitious roots on the stolon base and allocating more biomass to leaves on the stolon apex \citep{yuanEffectsSandAccretion1993}. However, if the sand burial rate is over some threshold, the growth of sand dune species will be inhibited \citep{maunEffectsBurialSand1996, shiEffectsSandBurial2004}. Our field investigation showed that few \textit{S. littoreus} can be found on the leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a), which can be attributed to the excessive sand burial on both ramets and conjoint stolons of \textit{S. littoreus}. Absence of photosynthesis area, combined with the continuous depletion of reserves previously stored in the plants \citep{frosiniGlobalChangeResponse2012}, finally lead to the failure of \textit{S. littoreus} escaped from excessive sand burial on leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a).  Similarly, if the sand burial rate is below some threshold, the species that can not withstand the severe sand burial will co-occur with those resistant to it. We found that low to moderate sand burial treatments had no significant impact on the stolon extension of \textit{S.littoreus}, which will not favor its access to the more habitats for soil water and nutrition, and further weaken its advantages as the dominant species with the decrease of sand burial rate. This is also consistent with our field investigation, \textit{Oenothera drummondii}, an invasive species widely distributed on the stabilized dune in South China, is more frequently co-occurred with \textit{S.littoreus} on the nebkhas stabilized by \textit{C. equisetifolia} in our study area (Figure~\ref{fig:added}a).

@@

% An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
Thanks to Patrick Hesp for his assistance with editing our paper. Thanks to Yingling Zhang for his assistance with the field experiment.

>>>>

\label{Introduction-4}
% 这一段主要介绍老鼠乐与研究去意义
\textit{Spinifex littoreus}, a herbaceous plant, is the dominant species in coastal foredunes in South China. It often grows vigorously in the more dynamic foredune, while it declines in the more stabilized backdunes in similarity to its Australian and NZ cousins \textit{S. hirsutus} and \textit{S. sericeus} \citep{hespReviewBiologicalGeomorphological1989}. Its peak growth occurs in summer, with two growth forms, including elongation of horizontal stolons and upward growth of vertical ramets, which sprout out from the same vegetative reproduction, and usually can be recognized as the same ramets \citep{jacksonPopulationBiologyEvolution1985}. The leaf apex of \textit{S. littoreus} is very sharp and hard, which makes it difficult to be intruded, and is usually recognized as one of the excellent species for sand dune fixation in this region \citep{yangDiurnalvariationcharacteristics2017}. Frequent typhoons often occur in the growing season of this species in South China, which causes severe sand burial on \textit{S. littoreus}, particularly its stolons on nebkhas (a sand dune that forms around vegetation) forming the foredune zone \citep{yangDiurnalvariationcharacteristics2017}(Figure~\ref{fig:sample-pic}a). However, the tolerance capacity of this species to sand burial is still unclear at present, and how this species revitalized in the sand burial caused by frequent typhoon events in growing season. Furthermore, local government has planted an invasive species \textit{Casuarinas equisetifolia} for the stabilization of nebkhas originally formed by \textit{S. littoreus}, which causes severe damage to this native species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure~\ref{fig:sample-pic}b). Therefore, understanding the adaptive strategies of \textit{S. littoreus} to sand burial levels, and its role in the stabilization of coastal sand dunes are very crucial for the effective coastal dune management and conservation in South China.

\begin{figure}
  \centering
  \subfloat[\textit{S. littoreus} was buried after a typhoon.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/sand_buried_plants.png}}}\hspace{5pt}
  \subfloat[\textit{S. littoreus} nebkhas was eradicated and planted with \textit{C. equisetifolia}.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/damaged_trees.jpg}}}
  \caption{(a) Intensive sand burial on the \textit{Spinifex littoreus} nebkhas on Pingtan Island after typhoon Soudelor (1513) landed in Putian City, Fujian Province, China in August, 2015. (b) The nebkhas formed by \textit{Spinifex littoreus} was stabilized by the planting of an invasive species \textit{Casuarinas equisetifolia} seedlings on Pingtan Island, Fujian Province, China.} 
  \label{fig:sample-pic}
\end{figure}

\label{Introduction-5}
% 我们的研究假设和研究思路
% 我们认为不同的沙埋情形将改变植株的生长方式，是该植物能够适应台风带来的强烈沙埋的关键性因素。
In this study, we assume that the growth of \textit{S. littoreus} can be facilitated with the increase of sand burial, which is probably the key factor for this native plant to adapt to the intense sand burial caused by frequent typhoon events in growing season. Then, the vertical height of ramets, horizontal length of stolons, and biomass allocation of adventitious roots, stems and leaves on stolons of \textit{S. littoreus} under different sand burial levels were simulated and measured in a field experiment, in a growing season on Pingtan Island, Fujian Province, South China.

@@

\subsection{Methods}
Field experiments were carried out in July, 2016, in Tannan bay, Pingtan Island (Figure~\ref{fig:map}). One study belt without the interruption of animals, pollutants, and apparent human activities was selected in the center of the coastal sand dunes. 
Considering most of the \textit{S. littoreus} were distributed on the windward slope of nebkhas in mobile dunes belt, 35 healthy plants with uniform size were selected for study on this slope (Figure\ref{fig:leeward_swale}). All the observed plants can be well distinguished from surrounding plants, the height of vertical ramets and the length of stolons were all similar with each other before the burial treatments. Stolons of \textit{S. littoreus} on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stolon base to the stolon top. All plant species around the selected plants were manually cleared, and wooden frames $20 cm$ in height (similar to the height of stolons) were set around the selected plants. Later, all the observed plants were fixed with a label, and its serial number was recorded on the label and wooden baffles respectively in order to facilitate the periodic measurements later. The few adventitious roots present on the stolons of the observed plants were completely eliminated, the height of vertical ramets and length of stolons were measured separately before the experiments began. Later, all the plants were buried with sand nearby artificially (Figure~\ref{fig:diagram}, Table~\ref{tab:treatment}), While control groups (CG) were unburied throughout the experiments.

@@

\begin{figure}[!h]
  \centering
  \subfloat[Developmental period.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9b.jpg}}}\hspace{5pt}
  \subfloat[Stabilized period.]{%
  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9a.jpg}}}
  \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b). (Photo was taken in Pingtan Island)} 
  \label{fig:added}
\end{figure}

Extensive colonization of horizontal stolons after sand burial will facilitate the plants to increase its capacity for utilization of water and nutrition, which is especially critical for the establishment of plants in a resource-poor environment, such as coastal sand dunes, and further enhance their growth as the dominant species in coastal sand dunes \citep{divyasreeEcologicalStudyReproduction2019,mendoza-gonzalezBiologicalFloraCoastal2014}. Our results indicated that all sand burial treatments had a significant promotion on the  stolon growth, and complete sand burial had more obvious influence than half sand burial. Species usually stimulate their growing point according to the signal of the gravity signal stresses \citep{zhouAnalysisgrowthstrategy2015}, and increase their node number and internode length to escape this physical barrier \citep{maunEffectsBurialSand1996}. The stresses signal of gravity in complete sand burial was usually stronger than it in half sand burial \citep{wangAdvancesStudiesMorphological2005}. This was consistent with our field investigation, we found that the tall remets of \textit{S. littoreus} could intercept sand sediments, and its conjoint stolons were buried at different levels on nebkhas. The stolon length of \textit{S. littoreus} on nebkhas in developmental period was much longer than it in stabilized period, which can be attributed to the more dynamic sand movement on the fomer (Figure~\ref{fig:added}).

Production of adventitious roots on the stolons will enhance the capacity of plants to use limited soil water and nutrition, and change the biomass and growth rhythms of plants \citep{martinezResponsesDuneMosses1999,dechAdventitiousRootProduction2006}. Our results indicated that the adventitious roots were produced on the \textit{S. littoreus} stolons in most of the sand burial treatments, both total length and number of roots were increased compared with the CG treatments, which will facilitate their revitalization from sand burial caused by typhoon events. More adventitious roots were allocated to the stolon base after sand burial. Generally, sand burial depth is deeper on the stolon base than other stolon sections due to more sand sediments accumulated around the conjoint ramets, which will increase the capacity for root growth and can improve their access to soil water and nutrition \citep{yuanEffectsSandAccretion1993}. Moreover, \textit{S.littoreus} has a fibrous root system, and adventitious roots are initially produced from the primordium in the stolon node. However, only the primordium in the stolon base can develop well and finally break through the cuticular layer to produce the adventitious roots \citep{hochholdingerWeedsCropsGenetic2004}.

@@

% 凭借上述机制，我们的结果表明老鼠楽能够有效在近地表被严重的沙埋情况下加速生长并存活下来。在热带和亚热带地区的海岸，频繁的台风常常为迎风坡带来数十厘米厚的沙埋，尽管这样的沙埋足以阻止大多数植物在此生长，但老鼠楽凭借其独特的适应能力在此占据来绝对优势。
Response of plants to sand burial is usually species specific, and the growth of plants will be enhanced under optimal sand burial rate \citep{noletUAVimagingModelGrowth2018}. We found that \textit{S.littoreus} can adapt to the severe sand burial caused by frequent typhoons in our study area, and will revitalize later by increasing the horizontal stolon length, producing abundant adventitious roots on the stolon base and allocating more biomass to leaves on the stolon apex \citep{yuanEffectsSandAccretion1993}. However, if the sand burial rate is over some threshold, the growth of sand dune species will be inhibited \citep{maunEffectsBurialSand1996, shiEffectsSandBurial2004}. Our field investigation showed that few \textit{S. littoreus} can be found on the leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a), which can be attributed to the excessive sand burial on both ramets and conjoint stolons of \textit{S. littoreus}. Absence of photosynthesis area, combined with the continuous depletion of reserves previously stored in the plants \citep{frosiniGlobalChangeResponse2012}, finally lead to the failure of \textit{S. littoreus} escaped from excessive sand burial on leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a).  Similarly, if the sand burial rate is below some threshold, the species that can not withstand the severe sand burial will co-occur with those resistant to it. We found that low to moderate sand burial treatments had no significant impact on the stolon extension of \textit{S.littoreus}, which will not favor its access to the more habitats for soil water and nutrition, and further weaken its advantages as the dominant species with the decrease of sand burial rate. This is also consistent with our field investigation, \textit{Oenothera drummondii}, an invasive species widely distributed on the stabilized dune in South China, is more frequently co-occurred with \textit{S.littoreus} on the nebkhas stabilized by \textit{C. equisetifolia} in our study area (Figure~\ref{fig:added}a and Figure~\ref{fig:leeward_swale}b).

@@

% An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
Thanks to Patrick Hesp for his assistance with editing our paper. Thanks to Zhiqiang Ye for his assistance with the field experiment.
